---
title: "KiN Experiment 1 Analysis"
output: html_notebook
---

## 1. Load libraries and download data from OSF

Load libraries 
```{r load libraries}
for (package in c("tidyverse", "dplyr", "jsonlite", "lme4", "here", "glue", "utils")) {
  suppressWarnings(
    suppressPackageStartupMessages(
      library(package, character.only = TRUE)
      )
    )
}
```

Download data from OSF 
```{r download data from osf}
get_raw_data <- function(osf_address) {

  print(glue("\nDownloading data\n"))

  zip_path <- here("Experiment 1", "data", "raw_data.zip")

  glue::glue("https://files.osf.io/v1/resources/{osf_address}/providers/osfstorage/?zip=") %>%
    curl::curl_download(zip_path, quiet = FALSE)

  utils::unzip(
    zip_path,
    overwrite = TRUE,
    exdir = fs::path_ext_remove(zip_path)
  )

  file.remove(zip_path)
}

#specify OSF path
osf_path <- "uj3tw"
file_name <- "Exp1_data"
data_directory <- here("Experiment 1", "data")
raw_data_directory <- here("Experiment 1", "data", "raw_data")
processed_data_directory <- here("Experiment 1", "data", "processed_data")



# create data folder if it does not yet exist
if (!dir.exists(data_directory)) {
  dir.create(data_directory, recursive = TRUE)
} else {
  print("Data Directory already exists!")
}

# as long as there isn't already an existing folder download the raw data
if (!dir.exists(raw_data_directory)) {
  get_raw_data(osf_path)
} else {
  print("Raw Data Directory already exists!")
}

# as long as there isn't already an existing folder create a processed data folder
if (!dir.exists(processed_data_directory)) {
  dir.create(processed_data_directory, recursive = TRUE) 
} else {
  print("Processed Data Directory already exists!")
}
```


## 2. Data Processing

Data cleaning 
```{r data processing} 

# warmup, scenario, conditions, responses, attention check questions  
participant_data <- function(csv) {
  data <- read.csv(csv) %>%
  mutate(participant_id = fromJSON(.$response[2])[[1]]) %>%
  filter(trial_type %in% c('KiN_response', 'survey-text', 'html-button-response')) %>%
  # some participants may have done two warmups
  {if (nrow(.) > 22) slice(., -(1:3)) else slice(., -(1:2)) } %>%
  mutate(row_num = row_number())

  participant_data <- bind_cols(
    # attention check: about the explicit rule
    data %>%
      filter(trial_type == "survey-text") %>%
      transmute(participant_id, attn_check = sapply(response, function(x) fromJSON(x)[[1]])),
    
    # main dv: negotiation vs direct request 
    data %>%
      filter(trial_type == "KiN_response", row_num %in% c(3, 8, 13, 18)) %>%
      transmute(dv = response),
      
    
    # attention check: ask size
    data %>%
      filter(trial_type == "KiN_response", row_num %in% c(2, 7, 12, 17)) %>%
      transmute(ask_size_check = response, scenario, ask_size, interaction_history),

    # likelihood of response success (0: definitely yes, 1: maybe, 2: definitely not)
    data %>%
      filter(trial_type == "html-button-response") %>%
      mutate(pair = ceiling(row_number() / 2)) %>%
      group_by(pair) %>%
      summarise(
        direct_likelihood = response[which.min(nchar(stimulus))], # direct requests are shorter
        negotiation_likelihood = response[which.max(nchar(stimulus))], # negotiating requests are longer
        likelihood_q_order = which.min(nchar(stimulus)) # 1 if direct first, 2 if negotiating first
      ) %>%
      ungroup() %>%
      select(-pair)
    
  )
  return (participant_data)
}
```

Adding demographics
```{r adding demographics to processed data}
age <- read.csv("KiN_demographics.csv")
raw_data_directory <- here("Experiment 1", "data","raw_data")
processed_data_directory <- here("Experiment 1","data","processed_data")


all_data <- list.files(raw_data_directory, pattern = "*.csv", full.names = TRUE) %>%
  map_dfr(participant_data) %>% 
  filter(grepl("^p\\d{3}$", participant_id)) %>%
  left_join(age, all_data, by = "participant_id") %>%
  mutate(negotiating_request = as.integer(startsWith(dv, "If"))) %>%

  # exclude children younger than 3 and older than 8
  filter(age_day_of >= 4 & age_day_of <= 9)

# likelihood values are unintuitive (0: definitely, 1: maybe, 2: definitely yes)
# flipping so that its (0: definitely not, 1: maybe, 2: definitely yes)
all_data <- all_data %>%
      mutate(
        direct_likelihood = as.numeric(direct_likelihood),
    negotiation_likelihood = as.numeric(negotiation_likelihood),
        direct_likelihood = ifelse(direct_likelihood == 0, 2, ifelse(direct_likelihood == 2, 0, direct_likelihood)),
        negotiation_likelihood = ifelse(negotiation_likelihood == 0, 2, ifelse(negotiation_likelihood == 2, 0, negotiation_likelihood))
      )

write.csv(all_data, paste0(processed_data_directory, "/", "Exp1_processed_data.csv"))
```

Exclusion criteria 
```{r exclusion criteria}

warmup <- function(csv){
  data <- read.csv(csv) %>%
  mutate(participant_id = fromJSON(.$response[2])[[1]]) %>%
  filter(scenario == 'warmup')
  
  return (data)
}

exclusion <- list.files(raw_data_directory, pattern = "*.csv", full.names = TRUE) %>%
  map_dfr(warmup) %>% 
  filter(grepl("^p\\d{3}$", participant_id)) %>% 
  group_by(participant_id) %>%
  summarise(all_incorrect = all(correct == 'false'), .groups = "drop") %>%
  filter(all_incorrect) %>%
  pull(participant_id)

exclusion

# no participants excluded per exclusion criteria
```

## 3. Pre-registered Analyses 

```{r load data for analyses}
processed_data_directory <- here("..","data","processed_data")
all_data <- read.csv(paste0(processed_data_directory, "/", "Exp1_processed_data.csv"))
```

Main pre-registered analyses 
```{r main pre-registered analysis}
all_data <- all_data %>%
  mutate(
    magnitude_c = ifelse(ask_size == "small", -0.5, 0.5),
    interaction_history_c = ifelse(interaction_history == "none", -0.5, 0.5)
  )

# model fails to converge
model <- glmer(
  negotiating_request ~ magnitude_c + interaction_history_c + 
    (1 + magnitude_c + interaction_history_c | participant_id),
  data = all_data,
  family = binomial
)

summary(model)

# model (without slopes for interaction_history)
model2 <- glmer(
  negotiating_request ~ magnitude_c + interaction_history_c + 
    (1 + magnitude_c  | participant_id),
  data = all_data,
  family = binomial
)

summary(model2)

# model (without slopes for magnitude_c)
model3 <- glmer(
  negotiating_request ~ magnitude_c + interaction_history_c + 
    (1 | participant_id),
  data = all_data,
  family = binomial
)

summary(model3)
```

Secondary Analyses 
```{r secondary analyses}
all_data <- all_data %>%
  mutate(
    age_day_of = as.numeric(age_day_of),
    age_c = scale(age_day_of)[,1]
  )

# model fails to converge
age_effects_model <- glmer(
  negotiating_request ~ age_c * magnitude_c + age_c * interaction_history_c +
    (1 + magnitude_c + interaction_history_c | participant_id),
  data = all_data,
  family = binomial
)

summary(age_effects_model)

# age effect model without interaction_history slope
age_effects_model2 <- glmer(
  negotiating_request ~ age_c * magnitude_c + age_c * interaction_history_c +
    (1 + magnitude_c | participant_id),
  data = all_data,
  family = binomial
)

summary(age_effects_model2)

# age effect model without magnitude_c slope
age_effects_model3 <- glmer(
  negotiating_request ~ age_c * magnitude_c + age_c * interaction_history_c +
    (1 | participant_id),
  data = all_data,
  family = binomial
)

summary(age_effects_model3)

```



## 4. Figures

Load data 
```{r load data for figures}
processed_data_directory <- here("Experiment 1","data","processed_data")
all_data <- read.csv(paste0(processed_data_directory, "/", "Exp1_processed_data.csv"))

# just so that the condition orders make sense in the figure (small --> big; none --> failed)
all_data <- all_data %>%
  mutate(
    ask_size = factor(ask_size, levels = c("small", "big")),
    interaction_history = factor(interaction_history, levels = c("none", "failed"))
  )
```

Overall Averages
```{r}
# overall proportion of negotiating 
print("overall proportion of negotiating")
mean(all_data$negotiating_request, na.rm = TRUE)

# proportion of negotiation across scenarios 
ggplot(all_data, aes(x = scenario,
                     y = negotiating_request)) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
    stat_summary(fun = mean, geom = "text", position = position_dodge(width = 1), aes(label = round(after_stat(y), 2)), vjust = -1) +
  labs(
    title = "Proportion Negotiating Across Scenarios", 
    x = "Scenario", y = "Proportion Negotiating") +
  theme_light()

# proportion of negotiations across scenarios: ask_size x interaction_history
ggplot(all_data, aes(x = ask_size,
                     y = negotiating_request,
                     fill = interaction_history)) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
  facet_wrap(~ scenario) +
  scale_fill_manual(values = c("failed" = "#89B3F0","none" = "#F0D87F"))+
  labs(
    title = "Proportion Negotiating Across Scenarios and Conditions", 
    x = "Ask Size", y = "Proportion Negotiating",fill = "Interaction History") +
  theme_light()

# proportion of negotiations across scenarios x ask_size x interaction_history
ggplot(all_data, aes(x = ask_size,
                     y = negotiating_request,
                     fill = interaction_history)) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
  stat_summary(fun = mean, geom = "text", position = position_dodge(width = 1), aes(label = round(after_stat(y), 2)), vjust = -1) +
  # geom_hline(yintercept = mean(all_data$negotiating_request), color = "darkgrey", linetype = "dashed")+
  scale_fill_manual(values = c("failed" = "#89B3F0","none" = "#F0D87F"))+
  ylim(0,1) +
  labs(
    title = "Proportion Negotiating Across Conditons (n=50)", 
    x = "Ask Size", y = "Proportion Negotiating",fill = "Interaction History") +
  theme_light()


# age continous 
ggplot(all_data, aes(x=age_day_of, y=negotiating_request)) + 
    geom_smooth() +
  # geom_jitter() +
  labs(
    title = "Age Effects on Negotiating", 
    x= "Age (in years)", y="Proportion Negotiating"
  )+ 
  theme_light()

```
Effect of ask_size
```{r effect of ask size}
# proportion of negotiations across two manipulations of ask_size (small vs big)
ggplot(all_data, aes(x = ask_size,
                     y = negotiating_request)) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
  stat_summary(fun = mean, geom = "text", position = position_dodge(width = 1), aes(label = round(after_stat(y), 2)), vjust = -1) +
  ylim(0,1) +
  labs(
    title = "Proportion Negotiating across Magnitude of Ask (Small ask vs Big Ask)", 
    x = "Ask Size", y = "Proportion Negotiating") +
  theme_light()


# proportion of negotiations across ask_size and scenarios 
ggplot(all_data, aes(x = scenario,
                     y = negotiating_request,
                     fill = ask_size)) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
  scale_fill_manual(values = c("small" = "#EBAEC8","big" = "#9FEB73"))+
  labs(
    title = "Proportion Negotiating Across Scenarios and Conditions", 
    x = "Scenario", y = "Proportion Negotiating",fill = "Ask Size") +
  theme_light()

# ask size x age
age_summary_asksize <- all_data %>% 
  group_by(participant_id, age_day_of, ask_size) %>% 
  summarize(prop_negotiating = mean(negotiating_request), .groups="drop") 
age_summary_asksize$age_day_of <- as.numeric(as.character(age_summary_asksize$age_day_of))

# proportion of negotiation across ask_size and age 
ggplot(age_summary_asksize, aes(x = age_day_of, y = prop_negotiating, color = ask_size)) + 
  # ylim(0.25,1.25)+
  geom_smooth() +
  scale_color_manual(values = c("small" = "#E055A5","big" = "#9FEB73")) +
  labs(
    title = "Age and Ask Size Effects on Negotiating", 
    x = "Age (in years)", 
    y = "Proportion Negotiating"
  ) + 
  theme_light()

```
Effect of interaction_history
```{r effect of interaction history}

# proportion of negotiations across two manipulations of interaction_history (none vs failed)
ggplot(all_data, aes(x = interaction_history,
                     y = negotiating_request)) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
  stat_summary(fun = mean, geom = "text", position = position_dodge(width = 1), aes(label = round(after_stat(y), 2)), vjust = -1) +
  ylim(0,1) +
  labs(
    title = "Proportion Negotiating across Interaction History (none vs failed)",
    x = "Interaction History", y = "Proportion Negotiating") +
  theme_light()

# proportion of negotiation across interaction history and scenario 
ggplot(all_data, aes(x = scenario,
                     y = negotiating_request,
                     fill = interaction_history)) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
  scale_fill_manual(values = c("failed" = "#89B3F0","none" = "#F0D87F"))+
  labs(
    title = "Proportion Negotiating Across Scenarios and Interaction History", 
    x = "Scenario", y = "Proportion Negotiating",fill = "Interaction History") +
  theme_light()

# ask size x interaction_history
age_summary_interactionhistory <- all_data %>% 
  group_by(participant_id, age_day_of, interaction_history) %>% 
  summarize(prop_negotiating = mean(negotiating_request), .groups="drop") 
age_summary_interactionhistory$age_day_of <- as.numeric(as.character(age_summary_interactionhistory$age_day_of))


# proportion of negotiation across interaction_history and age 
ggplot(age_summary_interactionhistory, aes(x = age_day_of, y = prop_negotiating, color = interaction_history)) + 
  # ylim(0.25,1.25)+
  geom_smooth() +
  scale_color_manual(values = c("failed" = "#89B3F0","none" = "#F0D87F")) +
  labs(
    title = "Age and Interactio History Effects on Negotiating", 
    x = "Age (in years)", 
    y = "Proportion Negotiating"
  ) + 
  theme_light()


```


Do children negotiate consistently?
```{r}
# do children negotiate consistently 
consistency_data <- all_data %>%
  group_by(participant_id) %>%
  summarise(
    n_scenarios       = n(),                          # how many scenarios they saw (always 4)
    n_negotiated      = sum(negotiating_request),     # how many times they said yes (0–4)
    prop_negotiated   = mean(negotiating_request),    # proportion of yes responses (0–1)
    consistent        = n_negotiated == n_scenarios | n_negotiated == 0,  # TRUE if all-yes or all-no
       age_day_of       = first(age_day_of),             # add this line

     consistency_type  = case_when(
      n_negotiated == n_scenarios ~ "Always negotiated",  # said yes all 4 times
      n_negotiated == 0           ~ "Never negotiated",   # said no all 4 times
      TRUE                        ~ "Mixed"               # anything in between
    )
  )

consistency_summary <- consistency_data %>%
  count(consistency_type) %>%       # how many children fall into each category
  mutate(prop = n / sum(n))         # what proportion of the sample that is

print (consistency_summary)

```

Experimenter effects
```{r experimenter effects?}
 # Experimenter effects?
ggplot(all_data, aes(x = experimenter, y = negotiating_request)) +
  stat_summary(fun=mean, geom='bar', position = position_dodge()) +
  # geom_bar(stat = "identity", position = "dodge") +
  labs(title= "Experimeter Effects on Proportion of Negotiating Requests",
       y = "Proportion of Negotiating Requests", x = "Experimenter") + 
  theme_light()


ggplot(all_data, aes(x = experimenter, y = negotiating_request, fill=ask_size)) +
  stat_summary(fun=mean, geom='bar', position = position_dodge()) +
  scale_fill_manual(values = c("small" = "#EBAEC8","big" = "#9FEB73"))+
  # geom_bar(stat = "identity", position = "dodge") +
  labs(title= "Experimeter and Ask Size Effects on Proportion of Negotiating Requests",
       y = "Proportion of Negotiating Requests", x = "Experimenter") + 
  theme_light()

ggplot(all_data, aes(x = experimenter, y = negotiating_request, fill=interaction_history)) +
  stat_summary(fun=mean, geom='bar', position = position_dodge()) +
  scale_fill_manual(values = c("failed" = "#89B3F0","none" = "#F0D87F"))+
  # geom_bar(stat = "identity", position = "dodge") +
  labs(title= "Experimeter and Interaction History Effects on Proportion of Negotiating Requests",
       y = "Proportion of Negotiating Requests", x = "Experimenter") + 
  theme_light()
```

Attention Check (ask size)
```{r}
# checking if attention check for ask size was correct 
all_data <- all_data %>% 
  mutate(
    ask_size_check_correct = if_else(
      (ask_size == "small" & ask_size_check == "alittle") |
      (ask_size == "big"   & ask_size_check == "alot"),
      1, 0
    )
  )


# % of correct attention check
cat("% of correct attention check responses")
print(mean(all_data$ask_size_check_correct))

# % of correct attention check by ask size and scenario 
cat("Attention Check Accuracy by Ask Size and Scenario\n")
attn_check_summary <- all_data %>% 
  group_by(ask_size, scenario) %>% 
  summarize(accuracy = mean(ask_size_check_correct), .groups="drop")

print(attn_check_summary)


cat("% of correct attention check by ask size\n")
print(all_data %>% group_by(ask_size) %>% summarize(accuracy = mean(ask_size_check_correct), .groups="drop"))

cat("% of correct attention check by scenario\n")
print(all_data %>% group_by(scenario) %>% summarize(accuracy = mean(ask_size_check_correct), .groups="drop"))

# filtering out the observations with incorrect responses for attention check 
attn_check_filtered_asksize <- all_data %>% 
  filter(ask_size_check_correct == 1)

# average for ask size manipulations when the attention check question was correct
ggplot(attn_check_filtered_asksize, aes(x = ask_size,
                     y = negotiating_request)) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
  stat_summary(fun = mean, geom = "text", position = position_dodge(width = 1), aes(label = round(after_stat(y), 2)), vjust = -1) +
    geom_text(stat = "count", aes(label = paste0("n=", after_stat(count))), y = 0.05) +

  ylim(0,1) +
  labs(
    title = "Proportion Negotiating across Magnitude of Ask (Small ask vs Big Ask)",
    x = "Ask Size", y = "Proportion Negotiating") +
  theme_light()

# only observations that had correct attention check response 

ggplot(attn_check_filtered_asksize, aes(x = scenario, y = negotiating_request, fill = ask_size)) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position= position_dodge(width=1),  width = 0.2, alpha=0.4) +
  stat_summary(fun = mean, geom = "text", position = position_dodge(width = 1), aes(label = round(after_stat(y), 2)), vjust = -1) +
  
  scale_fill_manual(values = c("small" = "#EBAEC8","big" = "#9FEB73")) +
  labs(
    title = "Proportion Negotiating Across Scenarios and Conditions",
    x = "Scenario",
    y = "Proportion Negotiating",
    fill = "Ask Size"
  ) +
  theme_light()



```

Likelihood of success judgement
```{r likelihood}

# do children think that negotiations are more likely to yield a successful outcome? 
cat("likelihood of success for direct requests: ")
print(mean(all_data$direct_likelihood))

cat("\nlikelihood of success for negotiating requests: ")
print(mean(all_data$negotiation_likelihood))


# difference in likelihood of success judgement (direct vs negotiating) --> ask size
plot_likelihood <- function(x_var) {
  all_data %>%
    pivot_longer(cols = c(direct_likelihood, negotiation_likelihood),
                 names_to = "likelihood_type",
                 values_to = "likelihood") %>%
    mutate(likelihood_type = recode(likelihood_type,
                                    "direct_likelihood" = "Direct",
                                    "negotiation_likelihood" = "Negotiating")) %>%
    group_by(across(all_of(x_var)), likelihood_type) %>%
    summarise(
      mean = mean(likelihood, na.rm = TRUE),
      ci   = qt(0.975, df = n() - 1) * sd(likelihood, na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    ) %>%
    ggplot(aes(x = .data[[x_var]], y = mean, color = likelihood_type)) +
    geom_point(size = 3, position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = mean - ci, ymax = mean + ci),
                  width = 0.15, position = position_dodge(width = 0.5)) +
    ylim(0, 2)+
    scale_color_manual(values = c("Direct" = "#89B3F0", "Negotiating" = "#FFBF39")) +
    labs(
      title = paste("Direct vs. Negotiation Likelihood by", x_var),
      x = x_var, y = "Mean Likelihood", color = "Likelihood Type"
    ) +
    theme_light()
}

# usage
plot_likelihood("ask_size")
plot_likelihood("scenario")
plot_likelihood("interaction_history")



# do children think their own responses (direct vs negotiating) are going to be successful? 
all_data <- all_data %>%
  mutate(
    choice = ifelse(negotiating_request == 0, "direct", "negotiating"),
    choice_likelihood = ifelse(negotiating_request == 0, direct_likelihood, negotiation_likelihood)
  )

cat("Average likelihood of success for chosen request\n")
print(mean(all_data$choice_likelihood))

ggplot(all_data, aes(x = age_day_of, y = choice_likelihood, color = choice)) +
  geom_smooth() +
  scale_color_manual(values = c("direct" = "#89B3F0", "negotiating" = "#FFBF39")) +
  labs(
    title = "Likelihood of Success by Age and Choice Type",
    x = "Age (in years)",
    y = "Likelihood of Success",
    color = "Choice"
  ) +
  theme_light()

ggplot(all_data, aes(x = ask_size, y = choice_likelihood, color = choice)) +
  geom_point(position = position_dodge(width = 0.5), alpha = 0.3) +
  stat_summary(fun = mean, geom = "point", size = 3, position = position_dodge(width = 0.5)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.5)) +
  facet_wrap(~ scenario) +
  scale_color_manual(values = c("direct" = "#89B3F0", "negotiating" = "#FFBF39")) +
  labs(
    title = "Likelihood of Success by Ask Size, Choice, and Scenario",
    x = "Ask Size",
    y = "Likelihood of Success",
    color = "Choice"
  ) +
  theme_light()

all_data %>%
  # mutate(request_type = if_else(negotiating_request == 0, "Direct", "Negotiating")) %>%
  group_by(age_day_of) %>%
  summarise(mean = mean(choice_likelihood, na.rm = TRUE),
            ci = qt(0.975, df = n() - 1) * sd(choice_likelihood, na.rm = TRUE) / sqrt(n()),
            .groups = "drop") %>%
  ggplot(aes(x = age_day_of, y = mean)) +
  geom_smooth(aes(y = mean))+
  labs(y = "Mean Choice Likelihood", x = "Age", fill = "Request Type") +
  theme_light()


all_data %>%
  mutate(
    request_type = if_else(negotiating_request == 0, "Direct", "Negotiating"),
    likelihood_label = factor(choice_likelihood,
                              levels = c(0, 1, 2),
                              labels = c("Unlikely", "Neutral", "Likely"))
  ) %>%
  count(request_type, likelihood_label) %>%
  group_by(request_type) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = request_type, y = prop, fill = likelihood_label)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0("n=", n)),
            position = position_stack(vjust = 0.5),
            size = 3.5, color = "white", fontface = "bold") +
  scale_fill_manual(values = c("Unlikely" = "#E07B7B", "Neutral" = "#D4D4D4", "Likely" = "#89B3F0")) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Perceived Likelihood of Success for Own Choice",
    x = "Request Type", y = "Proportion", fill = "Likelihood"
  ) +
  theme_light()



```

```{r}
# to-do: filter out only first trial and see if there are main effects of ask size and interaction history and all other stuff
# note: it might be because of repetitions 
```





